### 2023-09-19 grants/ddirg/src/roberts_data_management.qmd
research ethics draft

A mockup of the flyers used in these treatments is are included in @fig-mockup.

@@

The data that I will collect in the study are all based on self-reported responses to questions I outline here. To maintain the privacy of the participants, none of them will be compelled to provide any data that they do not wish to share.

>>>>

A mockup of the first page of the flyers used in these treatments is are included in @fig-mockup.

@@

The data that I will collect in the study are all based on self-reported responses to questions I outline here. To maintain the privacy of the participants, none of them will be compelled to provide any data that they do not wish to share. The platform that I intend to recruit participants on will depend on funding sources, but recruitment and the administration of the study is likely to be done through Prolific.
